---
title: "Get ID maps"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


The `get_id_map()` function let's you enter IDs from multiple data sources to return a map of all those held by ROR. THis includes UKPRNs, GRID IDs and Wikidata IDs, amongst others.

```{r example-1, eval = T, echo = T}
library(ror)

data <- get_id_map("grid.8391.3") # Exeter's grid id

data

```

If you have several IDs you want to map, you can run them through using `lapply()`, or perhaps better off, `purrr::safely()` which will catch any errors you might throw up. __It is only recommended you take this approach if you have a relatively small number of IDs to map__. The response time for trying to do this with too many IDs will be very long. In this case you may be better off using `read_data_dump()` to get a full extract of the dataset.
```{r example-2, eval = T, echo = T}

#vector ids
ids <- c("grid.7340.0", "grid.5337.2")

#run
results <- purrr::map(
  .x = ids,
  .f = purrr::safely(function(x) get_id_map(id = x))
) |>
  purrr::map_df("result")

results

```
